Data summary and analysis procedure: dual RNA-seq of \textit{Eimeria falciformis} infected \textit{Mus musculus}

### 2016-08-08 figuresANDmanuscript/table_rc.tex
Manuscript changes while working on feature counts integration and simple csv output to be handed over between scripts

% latex table generated in R 3.3.0 by xtable 1.8-2 package
% Wed Jun 22 17:40:30 2016
\begin{table}[ht]
\centering
\begin{tabular}{lllll}
  \hline
Sample & Mouse transcripts & E. falciformis transcripts & Percentage E. falciformis & \#E. falciformis genes \\ 
  \hline
NMRI\_oocysts\_rep1 & 11676.000 & 108477484.000 & 99.989 & 5734.000 \\ 
  NMRI\_oocysts\_rep2 & 19024.000 & 126543533.000 & 99.985 & 5774.000 \\ 
  NMRI\_sporozoites\_rep1 & 13800.000 & 92259539.000 & 99.985 & 5808.000 \\ 
  NMRI\_sporozoites\_rep2 & 8702.000 & 21508353.000 & 99.960 & 5564.000 \\ 
  NMRI\_1stInf\_7dpi\_rep1 & 12532238.000 & 79648900.000 & 86.405 & 5894.000 \\ 
  NMRI\_1stInf\_7dpi\_rep2 & 94310278.000 & 154343046.000 & 62.072 & 5897.000 \\ 
  NMRI\_1stInf\_5dpi\_rep3 & 334671421.000 & 54022504.000 & 13.899 & 5794.000 \\ 
  NMRI\_2ndInf\_7dpi\_rep1 & 97221189.000 & 9927803.000 & 9.265 & 5865.000 \\ 
  NMRI\_1stInf\_5dpi\_rep1 & 204647381.000 & 18549727.000 & 8.311 & 5739.000 \\ 
  C57BL6\_1stInf\_5dpi\_rep2 & 32887009.000 & 250954.000 & 0.757 & 3946.000 \\ 
  NMRI\_2ndInf\_5dpi\_rep1 & 589643389.000 & 3752923.000 & 0.632 & 5602.000 \\ 
  NMRI\_1stInf\_5dpi\_rep2 & 316721928.000 & 1609009.000 & 0.505 & 5439.000 \\ 
  C57BL6\_2ndInf\_5dpi\_rep1 & 62053975.000 & 311900.000 & 0.500 & 4610.000 \\ 
  NMRI\_1stInf\_3dpi\_rep1 & 209723287.000 & 815820.000 & 0.388 & 5466.000 \\ 
  C57BL6\_1stInf\_5dpi\_rep1 & 65523435.000 & 217606.000 & 0.331 & 4259.000 \\ 
  Rag\_2ndInf\_5dpi\_rep1 & 85288323.000 & 224273.000 & 0.262 & 4251.000 \\ 
  Rag\_1stInf\_5dpi\_rep2 & 57192380.000 & 113673.000 & 0.198 & 2969.000 \\ 
  NMRI\_1stInf\_3dpi\_rep2 & 515516785.000 & 903330.000 & 0.175 & 5101.000 \\ 
  Rag\_1stInf\_5dpi\_rep1 & 71173382.000 & 73445.000 & 0.103 & 2748.000 \\ 
  NMRI\_2ndInf\_7dpi\_rep2 & 122999109.000 & 46700.000 & 0.038 & 2174.000 \\ 
  NMRI\_2ndInf\_3dpi\_rep2 & 106446839.000 & 34699.000 & 0.033 & 1901.000 \\ 
  NMRI\_1stInf\_0dpi\_rep1 & 229165002.000 & 31459.000 & 0.014 & 1380.000 \\ 
  NMRI\_2ndInf\_5dpi\_rep2 & 113957667.000 & 12692.000 & 0.011 & 539.000 \\ 
  NMRI\_2ndInf\_3dpi\_rep1 & 91352242.000 & 5355.000 & 0.006 & 121.000 \\ 
  NMRI\_2ndInf\_0dpi\_rep2 & 90681785.000 & 3738.000 & 0.004 & 62.000 \\ 
  Rag\_0dpi\_rep1 & 43414004.000 & 474.000 & 0.001 & 2.000 \\ 
  C57BL6\_0dpi\_rep1 & 53877840.000 & 491.000 & 0.001 & 2.000 \\ 
  C57BL6\_0dpi\_rep2 & 76753491.000 & 657.000 & 0.001 & 2.000 \\ 
  Rag\_0dpi\_rep2 & 80702547.000 & 730.000 & 0.001 & 3.000 \\ 
  NMRI\_2ndInf\_0dpi\_rep1 & 285032128.000 & 326.000 & 0.000 & 2.000 \\ 
   \hline
\end{tabular}
\end{table}

>>>>

% latex table generated in R 3.3.1 by xtable 1.8-2 package
% Mon Aug  8 11:22:42 2016
\begin{table}[ht]
\centering
\begin{tabular}{lllllllll}
  \hline
Sample & Sequencing method & batch & read mappings Mouse & read mappings E. falciformis & Percentage E. falciformis & dpi & challenged & \# E. falciformis genes \\ 
  \hline
NMRI\_2ndInf\_0dpi\_rep1 & GAII & 2 & 70489674.000 & 247.000 & 0.000 & 0dpi & Callenge & 1.000 \\ 
  Rag\_0dpi\_rep1 & hiseq & 3 & 18853850.000 & 443.000 & 0.002 & 0dpi & None & 2.000 \\ 
  C57BL6\_0dpi\_rep1 & hiseq & 3 & 25119348.000 & 457.000 & 0.002 & 0dpi & None & 2.000 \\ 
  C57BL6\_0dpi\_rep2 & hiseq & 3 & 34377133.000 & 608.000 & 0.002 & 0dpi & None & 2.000 \\ 
  Rag\_0dpi\_rep2 & hiseq & 3 & 35233327.000 & 676.000 & 0.002 & 0dpi & None & 2.000 \\ 
  NMRI\_2ndInf\_0dpi\_rep2 & hiseq & 3 & 40794245.000 & 3406.000 & 0.008 & 0dpi & Callenge & 51.000 \\ 
  NMRI\_2ndInf\_3dpi\_rep1 & hiseq & 3 & 40544287.000 & 4803.000 & 0.012 & 3dpi & Callenge & 95.000 \\ 
  NMRI\_2ndInf\_5dpi\_rep2 & hiseq & 3 & 48289181.000 & 10941.000 & 0.023 & 5dpi & Callenge & 407.000 \\ 
  NMRI\_1stInf\_0dpi\_rep1 & GAII & 1 & 55176243.000 & 17954.000 & 0.033 & 0dpi & None & 701.000 \\ 
  NMRI\_2ndInf\_3dpi\_rep2 & hiseq & 3 & 46171909.000 & 29548.000 & 0.064 & 3dpi & Callenge & 1580.000 \\ 
  NMRI\_2ndInf\_7dpi\_rep2 & hiseq & 3 & 51722265.000 & 40091.000 & 0.077 & 7dpi & Callenge & 1836.000 \\ 
  Rag\_1stInf\_5dpi\_rep1 & hiseq & 3 & 29982453.000 & 63024.000 & 0.210 & 5dpi & First & 2548.000 \\ 
  Rag\_1stInf\_5dpi\_rep2 & hiseq & 3 & 25297803.000 & 99000.000 & 0.390 & 5dpi & First & 2828.000 \\ 
  C57BL6\_1stInf\_5dpi\_rep1 & hiseq & 3 & 29319604.000 & 185969.000 & 0.630 & 5dpi & First & 4173.000 \\ 
  Rag\_2ndInf\_5dpi\_rep1 & hiseq & 3 & 37093621.000 & 192856.000 & 0.517 & 5dpi & Callenge & 4167.000 \\ 
  C57BL6\_1stInf\_5dpi\_rep2 & hiseq & 3 & 18062349.000 & 215696.000 & 1.180 & 5dpi & First & 3823.000 \\ 
  C57BL6\_2ndInf\_5dpi\_rep1 & hiseq & 3 & 25660184.000 & 262909.000 & 1.014 & 5dpi & Callenge & 4563.000 \\ 
  NMRI\_1stInf\_3dpi\_rep1 & GAII & 1 & 49993358.000 & 394384.000 & 0.783 & 3dpi & First & 5220.000 \\ 
  NMRI\_1stInf\_3dpi\_rep2 & GAII & 2 & 117791044.000 & 413051.000 & 0.349 & 3dpi & First & 4862.000 \\ 
  NMRI\_1stInf\_5dpi\_rep2 & GAII & 2 & 76419774.000 & 794570.000 & 1.029 & 5dpi & First & 5333.000 \\ 
  NMRI\_2ndInf\_5dpi\_rep1 & GAII & 2 & 143186486.000 & 1846840.000 & 1.273 & 5dpi & Callenge & 5533.000 \\ 
  NMRI\_2ndInf\_7dpi\_rep1 & hiseq & 3 & 41467146.000 & 8634201.000 & 17.233 & 7dpi & Callenge & 5875.000 \\ 
  NMRI\_1stInf\_5dpi\_rep1 & GAII & 2 & 47037087.000 & 8669701.000 & 15.563 & 5dpi & First & 5700.000 \\ 
  NMRI\_sporozoites\_rep2 & GAII & 0 & 8656.000 & 11470604.000 & 99.925 & environmental & environmental & 5513.000 \\ 
  NMRI\_1stInf\_5dpi\_rep3 & GAII & 0 & 83735624.000 & 27839458.000 & 24.951 & 5dpi & First & 5784.000 \\ 
  NMRI\_1stInf\_7dpi\_rep1 & GAII & 1 & 3310666.000 & 39400884.000 & 92.249 & 7dpi & First & 5932.000 \\ 
  NMRI\_sporozoites\_rep1 & GAII & 1 & 4334.000 & 43774401.000 & 99.990 & environmental & environmental & 5825.000 \\ 
  NMRI\_oocysts\_rep1 & GAII & 1 & 3805.000 & 49653065.000 & 99.992 & environmental & environmental & 5695.000 \\ 
  NMRI\_oocysts\_rep2 & GAII & 0 & 18524.000 & 71019860.000 & 99.974 & environmental & environmental & 5777.000 \\ 
  NMRI\_1stInf\_7dpi\_rep2 & GAII & 1 & 21699324.000 & 73539445.000 & 77.216 & 7dpi & First & 5943.000 \\ 
   \hline
\end{tabular}
\end{table}
